Do Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates Affect Rice Sheath Blight?

### 2018-04-22 analysis/paper/paper.Rmd
Add new references

Sheath blight disease (*Rhizoctonia solani* Kühn), anastamosis group 1 [(teleomorph: *Thanatephorus cucumeris* (A.B. Frank) Donk.] of rice is economically important worldwide and difficult to find resistance to the disease [@Srinivasachary2011]. Therefore management is usually a combination of cultural practices, which include nitrogen and water management (citation).

>>>>

Sheath blight disease (*Rhizoctonia solani* Kühn), anastamosis group 1 [(teleomorph: *Thanatephorus cucumeris* (A.B. Frank) Donk.] of rice is an economically important disease worldwide causing up to 25% yield losses [@Kumar2009]. The disease is best managed through an integrated disease management approach which includes fungicide applications [@Groth2008], nitrogen management [@Castilla1996, @Slaton2003, @Tang2007] and water management [@Castilla1996].
